Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-22 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank, in a comparison for a entire years weather data of simulation in order to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of solar PV systems. It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features. It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis. However, it does not performs optimization. Drawbacks of PVsyst: it does nor perform optimization therefore it needs the system sized in order to validated it, PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for few seconds. PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.

@@

Those specific results partially answers the \textit{EQ2}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e. the tool always tries to feed the given load with electricity $365$ days/year.

@@

@@

\begin{itemize}
  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise), therefore the sizing that was done "by hand" is not correct. Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce solution. Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
	\item Case study 3: only our approach produced the optimal solution because there is the requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%. Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 6:
	\item Case study 7:
\end{itemize}

%As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.
%
Comparing the optimization results with those the real-world, the author had four PV systems deployed and monitored since June $2018$ in a riverside community in State pf Amazonas, Brazil, with demands  similar to those of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are closer to the results from PV panel, controller and inverter presented by the proposed formal synthesis approach than that of HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}. However the solution presented for the battery bank is very different.

HOMER Pro suggests a value in kW for the inverters that is very close to the peak of every case study, and it is just a reference value and not a commercial value of the inverter employed. The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst. This is a clear advantage of the formal synthesis method.

>>>>

In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank, in a comparison for a entire years weather data of simulation in order to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of solar PV systems. It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features. It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis~\cite{PVsyst2017}. However, it does not performs optimization. Drawbacks of PVsyst: it does nor perform optimization therefore it needs the system sized in order to validated it, PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for few seconds. PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.

@@

Those specific results partially answers the \textit{EG2}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e. the tool always tries to feed the given load with electricity $365$ days/year.

@@

The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.

@@

\begin{itemize}
  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise), therefore the sizing that was done "by hand" is not correct. Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce solution. Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
	\item Case study 3: only our approach produced the optimal solution because there is the requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%. Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $85.65$\%. Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce feasible solution with the equipment list available. Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
\end{itemize}

Each simulation with PVsyst took 4 seconds. Overall, those comparison between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.

%As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.

HOMER Pro suggests a value in kW for the inverters that is very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed. The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst. This is a clear advantage of the formal synthesis method.
